%-------------------------------------------------------------------------------
%	EXPERIENCE
%-------------------------------------------------------------------------------
\cvsection{Experience}

\begin{cventries}
  \cventry
    {Senior Backend Developer}
    {WorkStream (California-based HR/Payroll Platform)}
    {Remote}
    {Jul 2024 -- Present}
    {
      \begin{cvitems}
        \item {Joined the Time Shift team to drive new feature development in a high-scale HR and payroll product.}
        \item {Collaborated with product managers to deliver functionality enhancing user experience and scalability.}
        \item {Focused on high-performance, resilient, and maintainable backend solutions.}
      \end{cvitems}
    }

  \cventry
    {Backend Developer}
    {Datature (AI Vision Startup)}
    {Singapore}
    {Aug 2022 -- Jun 2024}
    {
      \begin{cvitems}
        \item {Led the development of public APIs and SDKs enabling clients to upload/annotate assets and train/deploy ML models.}
        \item {Architected scalable backend systems deployed on Google Kubernetes Engine.}
        \item {Implemented API gateway policies with Kong, including key authentication and rate limiting.}
      \end{cvitems}
    }

  \cventry
    {Backend Developer}
    {StoreHub (New Retail Startup, Series A USD 8.9M)}
    {China}
    {Mar 2019 -- Aug 2022}
    {
      \begin{cvitems}
        \item {Developed payment services and integrated third-party payment systems (TNG, Stripe, GrabPay) across POS and online platforms.}
        \item {Migrated company infrastructure to microservices architecture using Kubernetes.}
        \item {Applied Domain-Driven Design (DDD) principles to improve maintainability and scalability.}
      \end{cvitems}
    }
\end{cventries}
